### 2020-01-02 docs/thesis-project/article.tex
Update article.tex

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{images/armresults.PNG}
\caption{Cloud-Server in-degree, Cloudcast \textit{vs.} ARM \cite{marriage_of_convinience}}
\label{fig:arm_results}
\end{figure}

\section{Data Redundancy and File Survivability}\label{sec:dataredundancy}
In distributed storage systems, not losing files is of the utmost importance. Particularly, since peer availability in P2P networks is ever-changing and not guaranteed, the availability and even durability of a file may be endangered. A \textbf{\textit{durable file}} is one that, once put into the system, is not lost due to failures, whereas availability means that a user can access it promptly. For clarity, an available file is durable, but the other way is not necessarily correct. Distributed systems as a whole, usually ensure durability by employing file-level or block-level \textbf{\textit{replication}}; alternatively, some systems adopt \textbf{\textit{erasure coding}} techniques (\textit{coding} for short) or a mixture of both approaches. Replication has the advantage of having a more straightforward and less resource-intensive recovery model, on the other hand, coding has a better \textit{expansion factor}, i.e., can provide the same or even increased durability at a lower storage overhead. Because our proposal focuses on the survivability of files in P2P networks, using swarm guidance, where resources may be limited, we care only about coding in the survey that follows, briefly mentioning some of the raised concerns and inherent disadvantages of this technique.

>>>>

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{images/armresults.PNG}
\caption{Cloud-Server in-degree, Cloudcast \textit{vs.} ARM}
\label{fig:arm_results}
\end{figure}

\section{Data Redundancy}\label{sec:dataredundancy}
In DFS, not losing data is of the utmost importance. Particularly, peer availability in P2P networks is ever-changing and not guaranteed, and thus, availability, and even durability of files are at risk. A \textbf{\textit{durable file}} is one that, once put into the system, is not lost due to failures, whereas availability means that a user can access it promptly. Durability is accomplished by employing file or block-level \textbf{\textit{replication}} or alternatively, using \textbf{\textit{erasure coding}} techniques (\textit{coding} for short). Hybrid approaches are also possible. Replication has the advantage of having a straightforward and less resource-intensive recovery model, on the other hand, coding has a better \textit{expansion factor}, i.e., can provide the same or even increased durability at a lower storage overhead. Because our proposal focuses on the survivability of files in P2P networks built on top of personal computers, using swarm guidance, where resources may be limited, we focus on surveying coding, mentioning raised concerns and inherent disadvantages of this technique.
